Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2023-06-07 ba_resubmit/response_to_reviewers2.tex

%	{\color{red}{I don't really understand his confusion. Why wouldn't the product of $u$ parameters be constant in $u$ and the data? Perhaps if I use $\mathcal{L}(Z_j| m, y, \Gamma_{.j})$, it might be clearer?}}}

%	In the second line of the derivation, we divide by the $u$ parameters for all of the records in $A$ (note the product outside of the fraction). This quantity does not depend on $Z_j$ and is constant in $u$ and $\Gamma_{.j}$.  This is easiest to see through the likelihood expressed at the level of the agreement patterns. We are also notating this likelihood as $\mathcal{L}(Z_j | m, u, \Gamma_{.j})$ to make it clear what is considered constant.
%	
%	\begin{align*}
%	 \mathcal{L}(Z_j | m, u, \Gamma_{.j})  &= \prod_{p=1}^P \prod_{i \in r_{p_j}} m(p)^{I(Z_j = i)}u(p)^{1 - I(Z_j = i)}\\
%	 &= \prod_{p=1}^P u(p) ^ {N_{p_j}} \prod_{i \in r_{p_j}} m(p)^{I(Z_j = i)}u(p)^{- I(Z_j = i)}\\
%	 &= \prod_{p=1}^P u(p) ^ {N_{p_j}} \prod_{i \in r_{p_j}} w_p^{I(Z_j = i)}\\
%	\end{align*} 
%where $w_p = \frac{m(p)}{u(p)}$. The term outside of the inner product does not depend on $Z_j$. Thus we have
%\begin{align*}
%	\mathcal{L}(Z_j | m, u, \Gamma_{.j})   \propto
%	\begin{cases} 
%		w_p,  & z_j \leq n_1; \\
%		1, &  z_j  = n_1 + j; \\
%	\end{cases} \label{eqn:z}\\
%\end{align*}
%
%REVISIT

	\pointRaised{R}{%
Appendix 8.2: Thank you for including the details on integrating out pi from the full
conditionals. They surprised me. I had assumed that the authors had integrated out pi in the
prior for Z, as this is what Sadinle (2017) had done to form the “beta prior for bipartite
matchings”. Does the alternate approach presented in this paper provide a different algorithm
than directly integrating the prior distribution? Is the presented alternative approach justified?}

\reply{%
	The reviewer raises important questions. The main difference between the full conditionals in Sadinle (2017) and ours is that for him, $Z$ is a partition, while for us, it is not. This is what required him to integrate out $\pi$ in the prior, and then sequentially update each component of the $Z$ vector.

	The approach we have is justified, as indicated in the proof provided. However, under closer review, we have determined that it is unnecessary. Without integrating out $\pi$, all paramaters are updated through a standard Gibbs sampler. Furthermore, in other work we are developing, we actually need samples of $\pi$ in different applications.

	We reran all case studies and simulation using samples of $\pi$ in the full conditional for $Z$, and found no difference in results. This is unsuprsing, because with high numbers of observations, the posterior of the beta distrubution is highly concentrated around its mean.

	Therefore, we have updated the paper with full conditionals for the standard Gibbs sampler. We leave the remark about marginalization in the Appendix to highlight the similarity to Sadinle's method.

%	
% {\color{red}{I really don't know how to answer this. I don't know how I would ''directly integrate" $\pi$, and I don't know if what I do is ''justified." Its kind of an intellectual relic to how I was originally thinking about the problem, and it reveals a quantity similar to what Sadinle was working with.
% 		
% It is theoretically more straightforward to just not integrate out $\pi$, and use samples from $\pi$ in Gibbs sampler like I do with all other parameters. Would that be too large a change at this stage?
%
% Without integrating out $\pi$, the full conditional is given on page 26 of the Appendix.}}
}

@@

\pointRaised{R}{%
	Third paragraph of Section 4.1: The authors claim they are computing “sufficient
	statistics”. What exactly are these statistics sufficient for?
	}

	\reply{%

We show in the revised Section 4.3 that $\tilde{\Gamma} = \{\mathcal{P}, \mathcal{R}, \mathcal{N} \}$ is a set of statistics that are sufficient for $m$, $u$, and $Z$.

{\color{red}{I drafted a whole bunch of material to argue more rigoursly that $\tilde{\Gamma} = \{\mathcal{P}, \mathcal{R}, \mathcal{N} \}$ is  set of sufficient statistics. If this argument seems weak, or is too much new material, I can also just keep what I had, and use less rigorous term "summary statistics" instead.}} \todo
}

### 2023-06-07 ba_resubmit/kundinger_resubmit2.tex
corrected SEI

Since each component $\gamma_{ij}^f$ is discrete, there are only finitely many possible realizations of the comparison vector $\gamma_{ij}$. Let $P$ be the number of patterns realized in $\Gamma$ and note that it is bounded above by $P^{*} = F + \prod_{f=1}^F L_f$, where we have noted the possibility of missing values. Note that this quantity is controlled by the modeller in their choices for $F$ and $L_f$, and does not scale with $n_A$ or $n_B$. To obtain a memory efficient representation of the data, we map the agreement pattern of each record pair to a unique integer. \cite{enamorado2019using} accomplished this through the hashing function
\begin{align}
	\label{eqn:hashing}
	h^{*}(i, j) = \sum_{f = 1}^F I(\gamma_{ij}^f > 0)2^{\gamma_{ij}^f + I(f>1)\sum_{d=1}^{f-1}(L_d -1)}.
\end{align}
We then map these integers to sequential integers $\{1, \ldots, P\}$. We refer to each unique agreement pattern as $h_p$, and to the set of unique agreement patterns as $\mathcal{P} = \{h_1, \ldots, h_P\}$. When the $(i,j)$ record pair exhibits agreement pattern $p$, we say $\gamma_{ij} = h_p$.

>>>>

Since each component $\gamma_{ij}^f$ is discrete, there are only finitely many possible realizations of the comparison vector $\gamma_{ij}$. Let $P$ be the number of patterns realized in $\Gamma$ and note that it is bounded above by $P^{*} =  \prod_{f=1}^F (L_f + 1)$, where we have noted the possibility of missing values. Note that this quantity is controlled by the modeller in their choices for $F$ and $L_f$, and does not scale with $n_A$ or $n_B$. To obtain a memory efficient representation of the data, we map the agreement pattern of each record pair to a unique integer. \cite{enamorado2019using} accomplished this through the hashing function
\begin{align}
	\label{eqn:hashing}
	h^{*}(i, j) = \sum_{f = 1}^F I(\gamma_{ij}^f > 0)2^{\gamma_{ij}^f + I(f>1)\sum_{d=1}^{f-1}(L_d -1)}.
\end{align}
We then map these integers to sequential integers $\{1, \ldots, P\}$. We refer to each unique agreement pattern as $h_p$, and to the set of unique agreement patterns as $\mathcal{P} = \{h_1, \ldots, h_P\}$. When the $(i,j)$ record pair exhibits agreement pattern $p$, we say $\gamma_{ij} = h_p$.
